---
title: "PalmerPenguins"
author: "Batuhanep"
date: "2023-08-12"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

In this portfolio project, I will use the famous palmerpenguins dataset that I learned through Google Data Analytics program. 
About the data: Data were collected and made available by Dr. Kristen Gorman and the Palmer Station, Antarctica LTER, a member of the Long Term Ecological Research Network.

## Installation of Palmerpenguins.

```{r}
library(palmerpenguins)
library(tidyverse)
```

```{r}
head(penguins)
```

Note: We can also use summary(), str(), glimpse() and colnames() functions to summarize the data.

Let's say we want to know statistical summary of the data:

```{r}
summary(penguins)
```

## Installing skimr and janitor

```{r}
library(janitor)
library(skimr)
skim(penguins)
```

Let's create a new dataframe by arranging the data by flipper length in a descending order, this way we can preview the relationships between columns.

```{r}
flipper_length_arrange <- arrange(penguins, desc(flipper_length_mm))
```

In this step, I will create a new dataframe that shows details for only Adelie.

```{r}
adelie_penguins <- filter(penguins, penguins$species=="Adelie")
```

Let's say we only want to see body mass for each species and islands by using pipe.

```{r pipe}
islands_penguins <- penguins %>% select(species, island, body_mass_g)
```

# Visualisation by Using Ggplot2

```{r}
library(ggplot2)
```

Let's start with basic visualization showing the relationship between body mass and flipper length and more.

```{r}
ggplot(data = penguins) +
  geom_point(mapping = aes(x=flipper_length_mm, y=body_mass_g,color=species))+
  labs(title =  "Body mass and flipper length")
```

Let's create graphs showing flipper lengths for each species separately.

```{r}
ggplot(data = penguins) +
  geom_bar(mapping = aes(x=flipper_length_mm,fill=species)) + facet_wrap(~species)
```

We can also use geom_smooth to show relationship between body mass and flipper length.

```{r}
ggplot(data = penguins) +
  geom_smooth(mapping = aes(x=flipper_length_mm, y=body_mass_g,color=species))
```

Plus, we can combine both together.

```{r}
ggplot(data = penguins) +
  geom_point(mapping = aes(x=flipper_length_mm, y=body_mass_g,color=species)) +
  geom_smooth(mapping = aes(x=flipper_length_mm, y=body_mass_g,color=species)) +
  labs(title =  "Body mass and flipper length",subtitle="This graph shows the relationship between body mass and flipper length for each species") 
```

If we want to see how many species there are on each year:

```{r}
ggplot(data = penguins) +
  geom_bar(mapping = aes(x=year,fill=species))+
  labs(title = "Species for each year") +
  facet_wrap(~species)
```

References : - <https://doi.org/10.1371/journal.pone.0090081> Ecological Sexual Dimorphism and Environmental Variability within a Community of Antarctic Penguins (Genus Pygoscelis) Kristen B. Gorman ,Tony D. Williams,William R. Fraser -Google Data Analytics Professional Certificate, Data Analysis with R Programming.
